Papers

### 2023-01-06 quarto/index.qmd
update

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
	*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
	In *arXiv*, 2022<br>

>>>>

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
	<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
	*"Don't assign the same parameter-efficient fine-tuning strategy to different layers."*
	In *arXiv*, 2022<br>
	<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
